PropOcData2

### 2021-09-07 R/PropOc Data 3D.Rmd
minimal changes to adaptive threshold, PropOc Data and PropOC functions

```{r setup, include=FALSE}
library(pixmap)
library(rtiff)
library(reshape2)
library(gplots)
library(gdata)
library(plyr)
library(dplyr)
library(ggplot2)
library(cowplot)
library(tidyr)
library(purrr)
library(plotrix)
library(ggsignif)
library(rdist)
library("vcd")#this is fro fitting models to data
library(viridis)#color palette
library(gganimate)#gifs for ggplot

>>>>

```{r setup, include=FALSE}
library(pixmap)
library(rtiff)
library(reshape2)
library(gplots)
library(gdata)
library(plyr)
library(dplyr)
library(ggplot2)
library(cowplot)
library(tidyr)
library(purrr)
library(plotrix)
library(ggsignif)
library(rdist)
library("vcd")#this is fro fitting models to data
library(viridis)#color palette
library(gganimate)#gifs for ggplot
library(stringr)
